Parallelizing Linear Recurrent Neural Nets Over Sequence Length

### 2018-04-29 poster/main.tex
Add to 3rd column of poster

\author{Eric Martin and Chris Cundy} % Author(s)

\institute{FILL IN INSTITUTES} % Institution(s)

@@

Given $x_t$, $\lambda_t$ can compute $h_t=\lambda_t h_{t-1} + x_t$ for $t=1\ldots T$ on $p$
processors in $O(T/p + \log(p))$ with the classic parallel scan algorithm. Backpropagation
of gradient can also be parallelized with the same algorithm. We implemented a parallel linear
recurrence operation in CUDA and integrated it with TensorFlow.
\end{block}

@@

\begin{block}{Synthetic Long-Term Dependency}

  We tested the GILR-LSTM by comparing to the CuDNN LSTM implementation
  on a synthetic memorisation task (problem 2b from %\citet{hochreiter1997long}. )
  We compared the performance on variants with different values of
  \(n\).  We obtained speedups of over 6x measured in wall clock time to
  convergence.  Further, the GILR-LSTM attained convergence
  when the time dependence of the problem had a length of \textbf{one  million time steps}.

 \vspace{2em}
\begin{figure}
\includegraphics[width=1.0\linewidth]{8k_for_poster.png}
\caption{Accuracy on the memorisation task with 8,192 sequence length}
\end{figure}

@@

Nunc tempus venenatis facilisis. \textbf{Curabitur suscipit} consequat eros non porttitor. Sed a massa dolor, id ornare enim. Fusce quis massa dictum tortor \textbf{tincidunt mattis}. Donec quam est, lobortis quis pretium at, laoreet scelerisque lacus. Nam quis odio enim, in molestie libero. Vivamus cursus mi at \textit{nulla elementum sollicitudin}.

@@

\begin{center}
\begin{tabular}{ccc}
\includegraphics[width=0.4\linewidth]{logo.png} & \hfill & \includegraphics[width=0.4\linewidth]{logo.png}
\end{tabular}
\end{center}

>>>>

\author{Eric Martin and Chris Cundy*} % Author(s)

\institute{*UC Berkeley} % Institution(s)

@@

Given $x_t$, $\lambda_t$ can compute $h_t=\lambda_t h_{t-1} + x_t$ for $t=1\ldots T$ on $p$
processors in $O(T/p + \log(p))$ with the classic \textbf{parallel scan algorithm}. Backpropagation
of gradient can also be parallelized with the same algorithm. We implemented a parallel linear
recurrence operation in CUDA and integrated it with TensorFlow.
\end{block}

@@

\begin{block}{Learning Long-Term Dependencies}

Problem: Learn to remember 1 bit of information for $T$ time steps.

\vspace{1ex}
We measured time until convergence for a 2 layer GILR-LSTM and LSTM for $T$ ranging from
1,000 to 1,000,000.

\vspace{1ex}
The GILR-LSTM converged in over \textbf{6x} less wall time. We demonstrated a
GILR-LSTM could learn a \textbf{one million time step} sequential dependency, which
is at least a 100x longer dependency than previously learned.

\vspace{2ex}
\begin{figure}
\includegraphics[width=1.0\linewidth]{8k_for_poster.png}
\caption{Accuracy on the memorization task with 8,192 sequence length}
\end{figure}

@@

Parallel linear recurrence enables rapid learning on extremely long sequences at small
minibatch sizes. A significant portion of deep learning's current success can be
attributed to highly efficient matrix multiplication and convolution kernels.
We hope that parallel linear recurrence can join these algorithms and
be to large scale sequence
modelling what fast convolution algorithms are to image recognition.

\vspace{1ex}
Possible future work includes parallel training of memory augmented models, applications
to autoregressive flows, and replacing decay vector $\lambda_t$ with structured matrix
$\Lambda_t$.

@@
